Project Report: \\ Detecting Spam on Social Networking Sites

### 2012-05-08 docs/paper/paper.tex
Paper: data set section update

Currently, the site combats spam and other Terms of Service violations through volunteer moderators. Users can report content, including private messages, profiles and photographs to moderators, using a form that includes a drop-down menu of pre-selected reasons with the option to add a more detailed message in a text field. Likewise, the message interface allows a user to report a private message spam with a single click. Moderators have access to a queue of these reports. In addition to the material being reported, moderators are able to make decisions based on the data from the reported user's account, including outgoing private messages, IP addresses, as well as a list of other users who have logged in from the same computer (determined via IP address as well as by browser fingerprints). Moderators can then decide to delete the user, send a warning, or clear reports on a user. All moderator actions require them to annotate their decision with a brief log message.

@@

@@

To simplify the labeling of ham messages, we made the assumption that messages remaining in the inboxes of active users after a period of several months would most likely not be spam. Consequently, we extracted a working set of 2 million ham messages

>>>>

Currently, the site combats spam and other Terms of Service violations through volunteer moderators. Users can report content, including private messages, profiles and photographs to moderators, using a form that includes a drop-down menu of pre-selected reasons with the option to add a more detailed message in a text field. Likewise, the message interface allows a user to report a private message spam with a single click. Moderators have access to a queue of these reports. In addition to the material being reported, moderators are able to make decisions based on the data from the reported user's account, including outgoing private messages, IP addresses, as well as a list of other users who have logged in from the same computer (determined via IP address as well as by browser fingerprints). Moderators can then decide to delete the user, send a warning, or clear reports on a user. All moderator actions require them to annotate their decision with a brief log message. When deleting a user, moderators have the option of flagging the reported message (if there is one) as spam, or of flagging all of the user's outgoing private messages as spam.

@@

At the beginning of this research project, there were just over two million messages that had been flagged by moderators as spam. We extracted the contents of exactly two million of these messages from the site's database and merged them with records of account information for the deleted users who had sent the messages. In addition to using SQL to extract much of this information, we wrote Perl scripts to clean the data, tokenize messages and prepare data for further processing. The methodology section (X) offers more details on precisely which items of data were collected and why.

@@

Unlike spam messages, we did not have access to a comparable corpus of human-labeled ham messages. To simplify the labeling of ham messages, we made the assumption that messages remaining in the inboxes of active users after a period of several months would most likely not be spam. Consequently, we extracted a working set of 2 million ham messages that were sent in the beginning of January, 2012 and still existed in the recipient's inbox. To reduce the possibility of collecting messages sent by uncaught spammers to inactive or dormant users, we selected messages only from users and to recipients who had logged in within the last two weeks. As in the case of spam, we collected two million messages with associated account data and merged them into text files for feature extraction.
